%-------------------------
% Resume in Latex
% Author : 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{accsupp}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Ensure that generate pdf is machine readable/ATS parsable
\input{glyphtounicode}
\pdfgentounicode=1

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{blue}\titlerule \vspace{-5pt}]


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Ashutosh Narang} \\ \vspace{1pt}
    \small +91-831-963-9312 $|$ \href{mailto:ashutoshnarang80@gmail.com}{\underline{Email Me}} $|$ 
    \href{https://www.linkedin.com/in/ashutosh-narang/}{\underline{Connect With Me On LinkedIn}} 
    $|$ \href{https://ashutoshnarang.substack.com}{\underline{Read My Newsletter}}
    $|$ \href{https://twitter.com/conscioustahoe}{\underline{Follow Me On Twitter}}
    $|$ \href{https://github.com/conscioustahoe}{\underline{Github}}
    
\end{center}

%-----------SUMMARY-----------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{ I am a Senior Software Engineer with 5+ years of experience in designing and implementing backend systems and ML pipelines. I have a proven track record of delivering successful projects using a combination of strong technical expertise, understanding of consumer needs and mentoring abilities.}
    }
 \end{itemize}
    
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {Java14, Golang, Python3, Spring, PyTorch, Scikit-Learn, Machine Learning Algorithms, AWS, GCP, Kubernetes, Kafka, Redis, PostgreSQL, MongoDB, Google Collab, iOS Development, Swift, JavaScript, Node.JS}
    }}
 \end{itemize}
 
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Senior Software Engineer}{August 2021 – Present}
      {Palo Alto Networks Inc.}{}
      \resumeItemListStart
      \resumeItem{Led a team of 3 to build a highly-scalable platform based on Kafka Connect for data processing from multiple sources. Resulting platform is the backbone of products generating \$10+ million in revenue in total.}
      \resumeItem{Redesigned legacy batch service using SQS into kubernetes-based streaming service using Kafka, resulting in a 3000\% improvement in avg. throughput/sec.}
      \resumeItem{Wrote nearly 200 pages of internal documentation, topics ranging from engineering best practices, processes, how-tos for resolving production issues and code knowledge.}
      \resumeItemListEnd

    \resumeSubheading
      {Founding Engineer}{January 2021 – August 2021}
      {Gamma AI (Acquired By Palo Alto Networks Inc.)}{}
      \resumeItemListStart
      \resumeItem{Developed significant portions of tech including a high-performance event streaming system using Kafka and Kubernetes and cloud infra utilizing GCP, Terraform, and Helm.}
      \resumeItem{Developed a model for identifying secrets in source code repositories, leading to the inclusion of Version Control System in our portfolio of apps and resulting in successful deals with startups such as Scale.AI and Chime.}
      \resumeItem{Reduced latency of slow APIs from an avg. of 5 sec to 100 ms by explain-analyze db queries and applying correct indexes, vacuuming, tuning config params for effective caching and creating materialized views.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer}{March 2019 – Jan 2021}
      {Joveo}{}
      \resumeItemListStart
      \resumeItem{Implemented a novel system that publishes ads on Craigslist, w/o any available API and bypass bot detection. The service generated \$95K in monthly revenue and incurred a cost of only \$2K.}
      \resumeItem{Transformed the ad tracking system using a variety of technologies including API-Gateway, DynamoDB, Lambda, S3, Redshift, and SQS, processing nearly 150+ million events per day from 100+ jobs boards.}
      \resumeItem{Redesigned a high-frequency transaction service that buys ads and fetches performance metrics from Google and Facebook Ads, generating 15\% of the company's revenue.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Engineer}{April 2018 – March 2019}
      {NowFloats}{}
      \resumeItemListStart
      \resumeItem{Implemented a lot of business heavy APIs, engineered a caching layer based on Redis, improving API response time by 53\% and developed a secure wallet system for our marketplace to make purchases and reconciliation easier.}
      \resumeItemListEnd
      
     
    \resumeSubHeadingListEnd

%-----------PROJECTS AND WRITING-----------
\section{Projects And Writing}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small
    {\item{
     \textbf{{\href{https://www.notetakers.xyz/}{NoteTakers.xyz}}}{: Take margin notes while reading articles behind a paywall for free.}
    }}
    {\item{
     \textbf{Woof}{: iOS app to upload pics of your dogs and get AI generated images back like they're drawn by famous painters.}
    }}
    {\item{
     \textbf{{\href{https://ashutoshnarang.substack.com}{Ashutosh's Newsletter}}}{: I write about ai and engineering and have more than 1K subscribers.}
    }}
 \end{itemize}


% -----------PROJECTS-----------
% \section{Projects}

%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Nameko} \emph{Open-Source Contributor}}{}
%           \resumeItemListStart
%             \resumeItem{Nameko is a framework for building lightweight and highly scalable microservices in Python.}
%           \resumeItemListEnd

%     \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KIIT University}{2014 - 2018}
      {Bachelor in Computer Science and Engineering}{India}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
